---
title: "HW2"
author: "Rajath Prabhakar"
date: "2024-02-02"
output: html_document
---

```{r}
library(tidyverse)
```
Question 1

*1*

```{r}
nutrient <- read.table("nutrient.txt") %>% 
  rename(Observation = V1,
         Calcium = V2,
         Iron = V3, 
         Protein = V4, 
         VitaminA = V5, 
         VitaminC = V6)
```

```{r}
nutrient_summary <- nutrient %>% 
  summarize(Calcium_mean = mean(Calcium),
            Calcium_sd = sd(Calcium),
            Iron_mean = mean(Iron),
            Iron_sd = sd(Iron),
            Protein_mean = mean(Protein),
            Protein_sd = sd(Protein),
            VitaminA_mean = mean(VitaminA),
            VitaminA_sd = sd(VitaminA),
            VitaminC_mean = mean(VitaminC),
            VitaminC_sd = sd(VitaminC)) #%>% 
nutrient_summary_mean <- nutrient_summary %>% pivot_longer(cols = ends_with("_mean"), names_to = "Mean")
nutrient_summary_sd <- nutrient_summary %>% pivot_longer(cols = ends_with("_sd"), names_to = "SD")
```

*2*

Calcium
H0: Mean(Calcium) = 1000 
Ha: Mean(Calcium) < 1000

Iron
H0: Mean(Iron) = 15
Ha: Mean(Iron) < 15

Protein
H0: Mean(Protein) = 60
Ha: Mean(Protein) < 60

VitA
H0: Mean(VitA) = 800
Ha: Mean(VitA) < 800

VitC
H0: Mean(VitC) = 75
Ha: Mean(VitC) < 75

```{r}
t_test_calcium <- t.test(nutrient$Calcium, alternative = "less",mu = 1000)$p.value
t_test_iron <- t.test(nutrient$Iron, alternative = "less", mu = 15)$p.value
t_test_protein <- t.test(nutrient$Protein, alternative = "less", mu = 60)$p.value
t_test_VitA <- t.test(nutrient$VitaminA, alternative = "less", mu = 800)$p.value
t_test_VitC <- t.test(nutrient$VitaminC, alternative = "less", mu = 75)$p.value
p_value_table <- rbind(t_test_calcium, t_test_iron, t_test_protein, t_test_VitA, t_test_VitC)
p_value_table
```

*3*

For calcium and iron, there is sufficient evidence to reject the null hypotheses. US women do not meet the required amounts of calcium and iron. Their p-values, respectively, are 1.05e-104 and 3.33e-58. For protein, Vitamin A, and Vitamin C, there is insufficient evidence that US women fail to meet the required amounts for those nutrients. I would recommend that US women eat more foods that are rich in iron and calcium. 

Problem 2

a)

```{r}
multiple <-  read.table("multiple.txt")
```

```{r}
n = nrow(multiple)
p = ncol(multiple)
```

```{r}
alpha = 0.1
```

```{r}
mu_true <- c(rep(2,10), rep(0, 40))
mu_0 <- c(rep(0, 50))
```

```{r}
x_bar <- apply(multiple, 2, mean)
s2 <- apply(multiple,2,sd)
```

H0: M1 = M2 = ... = M50 = 0
Ha: At least one of these means does not equal 0

```{r}
tstat <- (x_bar - mu_0)/(s2/sqrt(n))
p_value <- 2*pnorm(-abs(tstat))
results_table <- as.data.frame(cbind(x_bar, p_value, mu_0, mu_true))
results_table <- results_table %>% 
  mutate(decision = case_when(
    p_value < 0.1 ~ "Reject",
    p_value >= 0.1 ~ "Fail to Reject"
  ))
results_table
```

b)

Type 1 error: concluding Mu != 0, but true means all equal 0 (rejecting H0 but H0 is true)
Type 2 error: concluding mu = 0, but mu != 0 (failing to reject H0 but H0 is false)

```{r}
results_table1 <- results_table %>% 
  mutate(error = case_when(
    mu_true == 2 & decision == "Reject" ~ "Rejected Correctly",
    mu_true == 2 & decision == "Fail to Reject" ~ "Type II Error",
    mu_true == 0 & decision == "Fail to Reject" ~ "Failed to Reject Correctly",
    mu_true == 0 & decision == "Reject" ~ "Type I Error"
  )) %>% 
  group_by(error) %>% 
  summarize(amount = n())
results_table1

```
Type 1 errors = 4, Type II errors = 0
Benjamin Hochberg Procedure

```{r}
xbar <- apply(multiple, 2, mean)
s <- apply(multiple, 2, sd)
```

```{r}
tstatistic <- xbar/(s/sqrt(100))
```

```{r}
p_value = 2*pnorm(-abs(tstatistic))
p_sort = data.frame("index"=1:50, "pvalue" = p_value)
p_sort <- p_sort %>% 
  arrange(pvalue)
p_sort
```

